An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-23 neurips-19/poly-embed.tex
Fixed notation for top k

\begin{theorem}
  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
\end{theorem}

@@

In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, the link function $\psi$ is exactly the link obtained from Theorem\raf{ref Bo's stuff} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
Thus, our framework would have simplified the process of finding such a link function.

To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem\raf{ref Bo's stuff} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
\begin{equation}\label{eq:abstain-link}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
In particular, Theorem\raf{ref Bo's stuff} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
It would be interesting to compare the two links in practice.

@@

\raf{Jessie: stuff to update / change:}
  \begin{itemize}
  \item Need to mention the link function typically used; don't see it anywhere
  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses
  \item Let's use our property notation; $\prop{L_2}$ instead of argmins
  \item The story we discussed: YK show $L_2$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?  (It also assures us that $L_2$ is consistent for something...)
  \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore
  \end{itemize}

@@

 In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$. (Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken}
Then, we show there is a discrete loss $\ell_2 : \{0,1\}^n \to \reals^\Y_+$ that is embedded by $L_2$.  (Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}

@@

We are given the surrogate 
\begin{align}\label{eq:L-2-surrogate}
L_2(u,y) := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
\end{align}
where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \argmin_{u' \in \reals^d} \inprod{p}{L_2(u)}$.
With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$, where $\R := \{r \subseteq 2^{[n]} : |r| \leq k \}$, given below:
\begin{align}\label{eq:ell-2}
\ell_2(r,y) &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
\end{align}
We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref for camera ready version}.
Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.

@@

Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.

First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\ell_2(\{y\}, p) = 2 (1-p_y) \geq 1$ by assumption on $p$. 
For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r,y) \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
Therefore, we have that $\vec{0} \in \argmin_{r' \subseteq [n]} \inprod{p}{\ell_2(r')}$ for any $p$ such that $\max_y p_y \leq 1/2$.

@@

Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}}\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}} and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

@@

  We first claim that for all $y \in \Y$, the minimum of $L(u,y)$ is achieved by some $u \in [0,1]^n$.
  Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \argmin_{u' \in \reals^d} L_2(u',y)$ so that $u \in [0,1]^n$.

@@

\begin{lemma}\label{lem:top-k-surrogate-embeds}
$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:2^{[n]} \to \reals^\Y_+$.
\end{lemma}
\begin{proof}
  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L_2(u)} = \min_{r \in \R}\inprod{p}{\ell_2(r)}$ for all $p \in \simplex$, and so we conclude that $L_2$ embeds $\ell_2$.
\end{proof}

>>>>

\begin{theorem}\label{thm:eps-thick-calibrated}
  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
  Then for small enough $\epsilon > 0$, the $\epsilon$-thickened link $\psi$ is well-defined and, furthermore, is a calibrated link from $L$ to $\ell$.
\end{theorem}

@@

In light of our framework, we can see that $L_{1/2}$ is an excellent example of an embedding, where $\varphi(y) = B(y)$ and $\varphi(\bot) = 0 \in \reals^d$.
Moreover, the link function $\psi$ is exactly the link obtained from Theorem~\ref{thm:eps-thick-calibrated} with the norm being $\|\cdot\|_\infty$ and $\epsilon=1/2$.
We show the full construction of $\Psi$ in Figure\raf{ref}, as well as a valid resolution yielding $\psi$.
Thus, our framework would have simplified the process of finding such a link function.

To illustrate this point further, we give an alternate link $\psi_1$ generated from Theorem~\ref{thm:eps-thick-calibrated} for $\|\cdot\|_1$ and $\epsilon=1$, shown in Figure\raf{ref}:
\begin{equation}\label{eq:abstain-link}
  \psi_1(u) = \begin{cases}
	\bot & \|u\|_1 \leq 1\\
	B^{-1}(\sgn(-u)) &\text{otherwise}
  \end{cases}~.
\end{equation}
In particular, Theorem~\ref{thm:eps-thick-calibrated} gives us calibration of $(L_{1/2},\psi_1)$ with respect to $\ellabs{1/2}$.
Aside from its simplicity, one possible advantage of $\psi_1$ is that it appears to yield the same constant in generalization bounds as $\psi$, yet assigns $\bot$ to much less of the surrogate space $\reals^d$.
It would be interesting to compare the two links in practice.

@@

\raf{Jessie: stuff to update / change:}
  \begin{itemize}
  \item Need to mention the link function typically used; don't see it anywhere
  \item You keep saying $L(r,y)$ not $L(r)_y$ for all losses \jessie{fixed}
  \item Let's use our property notation; $\prop{L_2}$ instead of argmins \jessie{fixed}
  \item The story we discussed: YK show $L_2$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L_2$ consistent?  (It also assures us that $L_2$ is consistent for something...)
  \item The next part of the story: oh look, $L_2$ embeds something which is $\ell_{top-k}$ plus some other term, so (a) we can see very clearly what $L_2$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.
  \item Domain of $\ell_2$ should not be $\{0,1\}^n$ anymore \jessie{fixed}
  \end{itemize}

@@

 In order to do this, we want to show that for all $p \in \simplex$, $\inf_{u' \in \reals^n} \inprod{p}{L_2(u')} = \min_{u' \in \{0,1\}^n} \inprod{p}{L_2(u')}$. (Lemma~\ref{lem:top-k-optimal-corners}.) \jessiet{Appendix ref will be broken}
Then, given the set $\R = \{r \subseteq 2^{[n]} : |r| \leq k\}$, we show there is a discrete loss $\ell_2 : \R \to \reals^\Y_+$ that is embedded by $L_2$.  (Lemma~\ref{lem:top-k-surrogate-embeds}.)\jessiet{Appendix ref will be broken}

@@

We are given the surrogate 
\begin{align}\label{eq:L-2-surrogate}
L_2(u)_y := \left( \frac{1}{k} \sum_{i=1}^k (u + \ones - e_y)_{[i]} - u_y \right)_+
\end{align}
where $x_{[i]}$ is the $i^{th}$ largest component of $x$.
By Lemma~\ref{lem:top-k-optimal-corners}\jessiet{in the Appendix... remove ref for camera ready version}, we can see that for all $p \in \simplex$, there is some $u \in \{0,1\}^n$ so that $u \in \prop{L_2(u)}$.
With this, we show that $L_2$ actually embeds the discrete loss $\ell_2: \R \to \reals^\Y_+$ given below:
\begin{align}\label{eq:ell-2}
\ell_2(r)_y &= \Ind{y \not\in r} + \frac{|r \setminus \{y\}|}{k}
\end{align}
We show that $L_2$ embeds $\ell_2$ in Lemma~\ref{lem:top-k-surrogate-embeds} \jessiet{in the Appendix... remove ref for camera ready version}.
Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we know $\risk{L_2} = \risk{\ell_2}$.

@@

Now to see a set of distributions where $\risk{L_2}(p) \neq \risk{\ell_{top-1}}(p)$, we claim that $\vec{0}~\in~\prop{\ell_2} \implies \risk{\ell_2}(p) = 1$ for any $p$ with $\max_y p_y \leq 1/2$.
Additionally $\risk{\ell_{top-1}}(p) = 1 - \max_y p_y < 1$.

First, $\ell(\vec{0}, \bar{p}) = 1$ for all $p \in \simplex$.
Taking the set $\{y\}$ for any $y \in \Y$, the expected loss $\inprod{p}{\ell_2(\{y\})} = 2 (1-p_y) \geq 1$ by assumption on $p$. 
For any $r$ such that $|r| \geq 2$ \jessiet{In general, $|r| \geq k+1$}, we know that  $\ell_2(r)_y \geq 1$ for all $y \in \Y$, so the expected loss much be greater than or equal to $1$.
Therefore, we have that $\vec{0} \in \prop{\ell_2}$ for any $p$ such that $\max_y p_y \leq 1/2$.

@@

Rather than formally define the Lov\'asz hinge, we defer the complete analysis to the full version of the paper,\footnote{Citation withheld for anonymity.\raf{And because it's not up yet!}} and focus here on the $k=2$ case.
For brevity, we write $g_\emptyset := g(\emptyset)$, $g_{1,2} := g(\{1,2\})$, etc.
%\raft{Jessie: I meant \emph{our} paper :-].  Leaving this here:\cite{yu2015lovaszarxiv}}
Assuming $g$ is normalized and increasing (meaning $g_{1,2} \geq \{g_1,g_2\} \geq g_\emptyset = 0$), the Lov\'asz hinge $L:\reals^k\to\reals^\Y_+$ is given by
\begin{multline}
  \label{eq:lovasz-hinge}
  L^g(u)_y = \max\Bigl\{(1-u_1y_1)_+ g_1 + (1-u_2y_2)_+ (g_{1,2}-g_1),\\[-4pt] (1-u_2y_2)_+ g_2 + (1-u_1y_1)_+ (g_{1,2}-g_2)\Bigr\}~,
\end{multline}
where $(x)_+ = \max\{x,0\}$.
We will explore the range of values of $g$ for which $L^g$ is consistent, where the link function $\psi:\reals^2\to\{-1,1\}^2$ is fixed as $\psi(u)_i = \sgn(u_i)$, with ties broken arbitrarily.

@@

  We first claim that for all $y \in \Y$, the minimum of $L(u)_y$ is achieved by some $u \in [0,1]^n$.
  Observe that if $u_{[1]} \geq u_{[n]} + 1$, the value of the loss gets ``cropped'' and will be the same by reporting $u_{[1]} = u_{[n]} + 1 = 1$. \jessiet{Flesh this out later.}
  Since $u_{[n]} = 0 \implies u_{[1]} \in [0,1]$, we can then observe there is some $u \in \prop{L_2}$ so that $u \in [0,1]^n$.

@@

\begin{lemma}\label{lem:top-k-surrogate-embeds}
$L_2:\reals^n \to \reals^\Y_+$ embeds $\ell_2:\R \to \reals^\Y_+$.
\end{lemma}
\begin{proof}
  We can verify $\ell_2(r) = L_2(\varphi(r))$ for all $r \subseteq [n]$ and $\varphi(r)$ being its conversion from a set to binary vector, so $\varphi(\R) = \{ u \in \{0,1\}^n : \|u\|_1 \leq k \}$.
  Moreover, by Lemma~\ref{lem:top-k-optimal-corners} and the above equality, respectively, we know that $\inf_{u \in \reals^n} \inprod{p}{L_2(u)} = \min_{u \in \varphi(\R)} \inprod{p}{L_2(u)} = \min_{r \in \R}\inprod{p}{\ell_2(r)}$ for all $p \in \simplex$, and so we conclude that $L_2$ embeds $\ell_2$.
\end{proof}
